%-------------------------
% Resume in Latex
% Author : Nathan Fleet
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://www.nathan-fleet.com/}{\Large Nathan Fleet}} & Email : \href{mailto:nfleet@kent.edu}{nfleet@kent.edu}\\
%   \href{https://www.nathan-fleet.com/}{https://www.nathan-fleet.com/} & Mobile : +1-330-541-6881 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Nathan Fleet} \\ \vspace{1pt}
    \small 330-541-6881 $|$ \href{mailto:x@x.com}{\underline{nfleet@kent.edu}} $|$ 
    \href{https://www.linkedin.com/in/nathan-fleet-555897217/}{\underline{linkedin.com/in/nathan}} $|$
    \href{https://github.com/nathanfleet}{\underline{github.com/nathan}} $|$
    \href{https://www.nathan-fleet.com/}{\underline{nathan-fleet.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kent state University}{Kent, OH}
      {Bachelor of Science in Computer Science}{Aug. 2021 -- Present}
  \resumeSubHeadingListEnd


%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Computer Science I A\&B Proc/Object Program}{CS13011/CS13012}
      {Familiarize students with programming in a high-level object-oriented language}{}
      \resumeItemListStart
        \resumeItem{Conditional and loop statements, functions, arrays, pointers}
        \resumeItem{Object classes, dynamic memory allocation, vectors}
      \resumeItemListEnd
    \resumeSubheading
      {Computer Science II: Data Structures/Abstraction}{CS23001}
      {Advanced computer programming design and development}{}
      \resumeItemListStart
        \resumeItem{Primary focus on data structures and abstraction}
        \resumeItem{Utilized an object-oriented programming language}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineering}{CS33901}
      {An introduction to software engineering concepts}{}
      \resumeItemListStart
        \resumeItem{life cycle models; modeling languages; requirements analysis; specification;}
        \resumeItem{design; testing; validation; project management and maintenance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Centralized Crypto} $|$ \emph{Next, React, Tailwind, Hot Toast}}{January 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Centralized Crypto is an application that allows users to deposit money into crypto currency accounts.}
            \resumeItem{Users are able to make deposits/withdraws from external bank accounts using the web application.}
            \resumeItem{Users are able to sign up with the “bank” to begin making transactions.}
            \resumeItem{Application utilizes json for the back-end}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Sneaker Sphere} $|$ \emph{SQL, React, Tailwind}}{January 2023 -- Present}
          \resumeItemListStart
            \resumeItem{The purpose of the Sneaker Sphere website is to create a marketplace for shoe buyers and sellers.}
            \resumeItem{By implementing an SQL database, the website is able to manage all necessary information in one place}
            \resumeItem{Application is an efficient and effective platform for shoe buying and selling.}
            \resumeItem{SQL database REST API, React front end}
          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Gamma Physics} $|$ \emph{JavaScript, HTML, CSS}}{January 2023 -- Present}
          \resumeItemListStart
            \resumeItem{This project implements the p5.js library, as well as HTML and CSS}
            \resumeItem{This game includes different levels, as well as different balls to choose from.}
            \resumeItem{The balls come in different shapes and follow different physics rules.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, SQL, JavaScript, HTML/CSS, R} \\
     \textbf{Frameworks}{: React, Node.js, Next.js} \\
     \textbf{Developer Tools}{: Git, VS Code, Visual Studio, Eclipse} \\
     \textbf{Libraries}{: p5.js }
    }}
 \end{itemize}

 %-----------SUMMARY-----------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     I'm a computer science student at Kent State University, currently enrolled in the honors college program. My academic interests lie in programming languages such as Python, JavaScript, and C++, and I enjoy using them to solve real-world problems. I'm passionate about software development and continuously strive to enhance my skills through hands-on experience and challenging coursework. I'm committed to developing innovative solutions that contribute to the betterment of society, and I'm excited about the opportunities that lie ahead as I continue to pursue my academic and professional goals.
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
