%-------------------------
% Resume in Latex
% Author : Nathan Fleet
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
% \titleformat{\section}{
%   \vspace{-4pt}\bfseries\scshape\raggedright\large
% }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\titleformat{\section}{
  \vspace{0pt}\bfseries\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemPlain}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\projectItem}[1]{
  \item\small{#1}
}

\newcommand{\projectSubHeading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label=\textbullet]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,label=\textbullet]}
\newcommand{\resumeItemListEnd}{\end{itemize}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge NATHAN FLEET}
\end{center}

\begin{center}
  \href{tel:+13305416881}{+13305416881} \, $\vert$ \,
  \href{mailto:nfleet@kent.edu}{nfleet@kent.edu} \, $\vert$ \,
  \href{https://github.com/yourusername}{https://github.com/nathanfleet} \, $\vert$ \,
  \href{https://linkedin.com/in/yourusername}{https://www.linkedin.com/in/nathan-fleet-555897217/} \, $\vert$ \,
  \href{https://nathan-fleet.com/}{https://www.nathan-fleet.com}
\end{center}

%-----------SUMMARY------------
\section{PROFESSIONAL SUMMARY}
  \small{A dynamic professional with a strong foundation in computer science and mathematics. Experienced in developing web and mobile applications. Seeking to leverage programming skills and problem-solving abilities to contribute to innovative software solutions.}

%-----------EXPERIENCE-----------------
\section{PROFESSIONAL EXPERIENCE}
  \begin{itemize}[leftmargin=0pt,label={}]
    \resumeSubheading
      {Kent State University}{Kent, OH}
      {Application Developer}{April 2024 -- Present}
      \resumeItemListStart
        \resumeItemPlain{}
          { Developed a location-based app using Flutter, similar to Life360, which displays users' live locations on a clock interface. }
        \resumeItemPlain{}
          { Implemented backend services with Supabase to manage user data and ensure real-time updates. }
        \resumeItemPlain{}
          { Collaborated with a team using Git and GitHub for version control, ensuring seamless integration and deployment. }
      \resumeItemListEnd
  \end{itemize}

%-----------EDUCATION-----------
\section{EDUCATION}
  \begin{itemize}[leftmargin=0pt,label={}]
    \resumeSubheading
      {Kent State University, Honors College}{December 2024}
      {Bachelor's, Computer Science, Mathematics}{GPA: 3.732}
  \end{itemize}
  
%-----------PROJECTS-----------
\section{PROJECTS \& OUTSIDE EXPERIENCE}
  \begin{itemize}[leftmargin=0pt,label={}]
    \projectSubHeading
      {\textbf{Centralized Crypto} $|$ \emph{Next, React, Tailwind}}{January 2023 -- May 2023}
      \resumeItemListStart
        \projectItem
          {Developed a cryptocurrency banking simulation application allowing users to make deposits and withdrawals from external bank accounts.}
        \projectItem
          {Implemented user authentication and transaction features using Next.js and React.}
        \projectItem
          {Utilized JSON for back-end data management, ensuring secure and efficient data handling.}
      \resumeItemListEnd
    \projectSubHeading
      {\textbf{Sneaker Sphere} $|$ \emph{SQL, React, Tailwind}}{January 2023 -- May 2023}
      \resumeItemListStart
        \projectItem
          {Created an online marketplace for buying and selling sneakers.}
        \projectItem
          {Designed and implemented a RESTful API with SQL database for efficient data management.}
        \projectItem
          {Developed front-end features in React for user registration, product listings, and transaction processing.}
      \resumeItemListEnd
    \projectSubHeading
      {\textbf{Gamma Physics} $|$ \emph{JavaScript, HTML, CSS}}{January 2023 -- May 2023}
      \resumeItemListStart
        \projectItem
          {Built an interactive physics-based game implementing different levels and customized game elements.}
        \projectItem
          {Utilized p5.js library to create dynamic graphics and physics simulations.}
        \projectItem
          {Enhanced user engagement through dynamic game-play and intuitive controls.}
      \resumeItemListEnd
    \projectSubHeading
      {\textbf{Choose Ohio First $|$ \emph{Computer Science Scholarship}}}{August 2021 -- December 2021}
      \resumeItemListStart
        \projectItem
          {Collaborated with professors and peers to develop an iOS application.}
        \projectItem
          {Participated in weekly meetings with guest speakers to enhance knowledge and prepare for conferences.}
      \resumeItemListEnd
  \end{itemize}

%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
    \small{\textbf{Skills}{: Python, C++, SQL, JavaScript, HTML/CSS, R Studio, React.js, Node.js, Next.js, Flutter, Git, VS Code, Visual Studio, p5.js, Supabase, Figma, Kanban, Excel/Sheets, Agile, Scrum}}

%-------------------------------------------
\end{document}